\documentclass[letterpaper, 10pt]{article}
\usepackage[left=2cm,right=2cm,top=1.75cm,bottom=1.75cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage[none]{hyphenat}
\usepackage{ltablex}

% Change itemize bullet type
\renewcommand{\labelitemi}{$\_$}
% Change itemize spacing
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

% TimeFrame
% #1 Start Year
% #2 End Year
% #3 Length of time
\newcommand{\timeFrame}[3] {
  \if\relax\detokenize{#2}\relax
    #1
    % {\space\space\space\space\space#1}
  \else
    #1 - #2
  \fi
  \newline
  \small \textit{#3}
}

%% Work experience
% #1 Employeer/Header
% #2 Title
% #3 Location
% #4 Description
% #5 Technologies used
\newcommand{\entry}[5] {
  % #1 Employeer/Header
  \textbf{#1}
  % #2 Title
  \if\relax\detokenize{#2}\relax
  \else
       - \textsc{#2}
  \fi
  % #3 Location
  \if\relax\detokenize{#3}\relax
  \else
      - \textsc{#3}
  \fi
  % #4 Description
  \newline #4
  % #5 Technologies used
  \if\relax\detokenize{#5}\relax
  \else
      \newline \textbf{Technology:} #5
  \fi
  \\
}

% Draw a horizontal line in the second column
\newcommand{\horizontalLine}[0] {
    \noindent\rule{.88\linewidth}{0.4pt}
}

\begin{document}
\pagenumbering{gobble}

\begin{tabularx}{\linewidth}{>{\hsize=.13\hsize}X>{\hsize=.87\hsize}X}

%% Header
{\bfseries\Large David McNeil} &
\href{https://github.com/davidMcneil}{https://github.com/davidMcneil}\newline
\href{mailto:mcneil.david2@gmail.com}{mcneil.david2@gmail.com}\newline
(314) 308-1596\\[10pt]

%% Profile
\textbf{Profile} &
{I am seeking a full time position applying the Rust programming language to the development of reliable and efficient software. I am an advocate of iterative design ensuring the continuous delivery of tested, documented, robust software. One of my greatest strengths is the ability to take a problem or technology, study it in general, focus in depth on relevant aspects, and distill this knowledge into a practical solution. Examples where I have applied this process include: machine learning, web development, and containerization frameworks.
} \\

%% Experience
\textbf{Experience} & \horizontalLine \\

% n~ask
\timeFrame{2016}{Present}{Three Years} &
\entry{n$\sim$ask incorporated}
  {Member of the Technical Staff}
  {Aurora, Colorado}
  {
  - Active Top Secret/Sensitive Compartmented Information (TS/SCI) clearance. \newline
  - Designed, developed, and maintained an operational system which ingests terabytes of data a day processed by several DSP and geolocation algorithms producing millions of results. The system runs using a containerized architecture consisting of hundreds of processes distributed on tens of machines located across the world. The system produces millions of metrics a day allowing for efficient monitoring and diagnostics. I created several web clients for management and visualization of the system as well as a native client used extensively by analysts. \newline
  - Developed a canvas based mapping library for efficiently rendering millions of features. \newline
  - Designed and developed the frontend for mission management software. \newline
  - Created a test harness for running hundreds of system tests in an analytics framework.
  }
  {C, C++, Docker, Go, InfluxDB, Java, Nomad, MongoDB, Python, Qt, React, Rust, TypeScript}

  % Indesign
\timeFrame{2014}{2015}{Three Months} &
\entry{Indesign, LLC}
  {Firmware Engineer Intern}
  {Indianapolis, Indiana}
  {- Developed an embedded system which interfaced with numerous sensors and actuators.}
  {C, Current Sensor, Hall Effect Sensor, MSP430, RFID, Servo Motor}

% NSWC
\timeFrame{2014}{2015}{Nine Months} &
\entry{Naval Surface Warfare Center}
  {Senior Design Project}
  {Crane, Indiana}
  {- Designed and developed a system to predict location based on RF spectrum data.}
  {GPS, Python, Software Defined Radio, SQLite}

% Garmin
\timeFrame{2013}{2014}{Three Months} &
\entry{Garmin Ltd.}
  {Low Level Software Engineer Intern}
  {Olathe, Kansas}
  {
  - Developed software for operating system profiling during route execution. \newline
  - Updated, maintained, and debugged extensive C/C++ code base.
  }
  {C, C++, Hardware Debugger}

% Cetani
\timeFrame{2012}{2013}{Three Months} &
\entry{Cetani}
  {Software Development Intern}
  {Carmel, Indiana}
  {
  - Developed a server for issuing hospital notifications and pushing real-time changes to front end user interfaces. \newline
  - Maintained and implemented new features in a Ruby on Rails application.
  }
  {C\#, HTML, CSS, Javascript, Node.js, Rails, Ruby, SQLServer}

% Oasis Digital
\timeFrame{2011}{2012}{Three months} &
\entry{Oasis Digital}
  {Software Development Intern}
  {Chesterfield, Missouri}
  {-Designed a work management system with a Node.js backend and responsive frontend.}
  {Backbone.js, CSS, HTML, Javascript, Node.js, PostgreSQL}


% Projects and Coursework work
\textbf{Projects  \& Coursework} & \horizontalLine \\

\timeFrame{2018}{}{Eighty Hours} &
\entry{Courier}
  {}
  {}
  {
  - A pub/sub service with an HTTP, JSON API and web based statistics and management page. \newline
  -Clients for C++, Go, Python, and Rust.
  }
  {Inferno.js, Rust, Typescript}

\timeFrame{2017}{}{Forty Hours} &
\entry{The Rusty Web}
  {}
  {}
  {
  - One of the first complete resources detailing how to integrate Rust, compiled to asm.js or WebAssembly, into a web application. \newline
  - Benchmarked implementations of the k-means clustering algorithm in different browsers.
  }
  {asm.js, JavaScript, Rust, WebAssembly}

\timeFrame{2015}{2016}{One Year} &
\entry{Master's Thesis}
  {}
  {}
  {- Developed a custom RISC instruction set architecture with assembler, compiler, and simulator.}
  {Bison, C++, Flex, LLVM}

\timeFrame{2015}{2016}{Thirty Weeks} &
\entry{Machine Learning}
  {}
  {}
  {
  - Developed a sunset image classifier, optical character recognition software, resistor classifier, and voice recognition software. \newline
  - Certification in machine learning from Stanford University.
  }
  {Lua, MATLAB/Octave, Neural Networks, Python, Support Vector Machines, TensorFlow, Torch}

\timeFrame{2015}{2016}{Ten Weeks} &
\entry{Artificial Intelligence}
  {}
  {}
  {- Study of search algorithms, reinforcement learning, machine learning, and applications.}
  {Natural Language Processing, Python}

\timeFrame{2015}{2016}{Ten Weeks} &
\entry{Compiler Construction}
  {}
  {}
  {- Developed a Java subset to LLVM bytecode compiler.}
  {ANTLR, Java, LLVM}

\timeFrame{2015}{2016}{Ten Weeks} &
\entry{DSP System Design}
  {}
  {}
  {
  - Study of finite word length effects in DSP systems. \newline
  - Implemented single sideband communication system.
  }
  {LabVIEW, MATLAB}

\timeFrame{2015}{2016}{Twenty Weeks} &
\entry{MEMS Modeling and Fabrication}
  {}
  {}
  {- Optimization of heat actuator process flow.}
  {Etchants, Electron Beam Evaporator, Photoresist Spinner, Mask Aligner}

\timeFrame{2012}{2015}{Ten Weeks} &
\entry{Data Structures and Algorithm Analysis}
  {}
  {}
  {- Intensive study of space and time trade-offs of using various data structures and algorithms.}
  {Java}

\timeFrame{2012}{2015}{Ten Weeks} &
\entry{Programming Language Concepts}
  {}
  {}
  {
  - Studied syntax, semantics, and design of programming languages. \newline
  - Implemented a Scheme interpreter.
  }
  {Scheme}

\timeFrame{2012}{2015}{Ten Weeks} &
\entry{Computer Networks}
  {}
  {}
  {- Developed an HTTP server dealing extensively with sockets and network communication state machines.}
  {C, C\#, Wireshark}

\timeFrame{2012}{2015}{Ten Weeks} &
\entry{Operating Systems}
  {}
  {}
  {- Created a bare metal operating system with: interactive shell, process scheduling and execution, and basic file manipulation.}
  {Bochs Emulator, C, Mips, x86}

\timeFrame{2012}{2015}{Twenty Weeks} &
\entry{Computer Architecture}
  {}
  {}
  {
  - Study of RISC architectures, DSP architectures, and modern, out-of-order processors. \newline
  - Designed and implemented a multicycle processor and assembly language.
  }
  {gem5 simulator, MIPS assembly, Spartan-3 board, Verilog, x86 assembly, }

\timeFrame{2012}{2015}{Thirty Weeks} &
\entry{Signals and Systems}
  {}
  {}
  {
  - Study of continuous and discreet time signals and systems. \newline
  - Design and analysis of filters and sampling methods.
  }
  {Electronics lab bench equipment, LabVIEW, Matlab}

\timeFrame{2012}{2015}{Twenty Weeks} &
\entry{Embedded Systems}
  {}
  {}
  {- Developed digital systems using PIC microcontrollers interfacing with digital and analog peripherals.}
  {C, PCB Design Software, PIC Assembly}

\timeFrame{2010}{}{One month} &
\entry{Ants AI Challenge}
  {}
  {}
  {- Placed 323 out of nearly 8000 contestants in an international programming contest to implement an algorithm controling a virtualized colony of ants.}
  {Python}

%    \timeFrame{2015}{2016}{Ten Weeks} &
%    \entry{Advanced Microcomputers}{}{}
%          {Developed systems which integrated FPGA and microprocessor components.}
%          {C, Verilog}
%
%    \timeFrame{2015}{2016}{Ten Weeks} &
%    \entry{Intro to Random Process Estimation}{}{}
%          {Study of techniques to analyze and characterize random processes.}
%          {MATLAB}
%
% \timeFrame{2012}{2013}{Forty Weeks} &
%    \entry{Circuit Design and Analysis}{}{}
%          {DC/AC Circuits, Electronic Device Modeling, Analog Electronics. Learned and put into practice circuit analysis and construction techniques.}
%          {Electronics lab bench equipment, SPICE}
%
% \timeFrame{2014}{2015}{Ten Weeks} &
%   \entry{Digital Systems}{}{}
%            {Designed combinational and sequential logic circuits using FPGAs. Developed system which interfaced over VGA to play simple game.}
%            {Verilog}
%
% \timeFrame{2015}{2016}{Ten Weeks} &
%    \entry{Mixed Signal Test and Product Engineering}{}{}
%          {Developed software capable of testing comparators, digital to analog converters, and analog to digital converters.}
%          {C, Automated Test Equipment}

%% Education
\textbf{Education} & \horizontalLine \\

% Masters (3.94 GPA)
\timeFrame{2015}{2016}{Ome Year} &
\entry{Rose-Hulman Institute of Technology}
  {}
  {Terre Haute, Indiana}
  {Master of Science in Electrical Engineering with a focus on computer architecture.}
  {}

% Bachlors  (3.64 GPA)
\timeFrame{2012}{2015}{Three Years} &
\entry{Rose-Hulman Institute of Technology}
  {}
  {Terre Haute, Indiana}
  {Bachelor of Science in Computer Engineering, Minor in Computer Science.}
  {}

\end{tabularx}

\vfill\hfill \today
\end{document}